### 2024-01-25 options/symbols_and_cmd.tex
Methodo (ES, UQ, brief RL) + Resultats mol_vs_atom

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A

@@

%% E
\newabbreviation[group={Acronyms}]{ESTD}{EnergyScope TD}{EnergyScope Typical Days}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{end-use demand}

@@

%% G
\newabbreviation[group={Acronyms}]{GHG}{GHG}{greenhouse gases}
\newabbreviation[group={Acronyms}]{GWP}{GWP}{global warming potential}

@@

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{non-energy demand}
\newabbreviation[group={Acronyms}]{NG}{NG}{natural gas}
\newabbreviation[group={Acronyms}]{NRE}{NRE}{non-renewable energy}
\newabbreviation[group={Acronyms}]{NSC}{NSC}{naphtha steam cracker}

@@

%% R
\newabbreviation[group={Acronyms}]{RE}{RE}{renewable energy}

%% S
\newabbreviation[group={Acronyms}]{SDGs}{SDGs}{Sustainable Development Goals}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{small modular reactor}

>>>>

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A
\newabbreviation[group={Acronyms}]{API}{API}{application programming interface}

@@

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{energy system optimisation models}
\newabbreviation[group={Acronyms}]{ESTD}{EnergyScope TD}{EnergyScope Typical Days}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{end-use demand}

@@

%% G
\newabbreviation[group={Acronyms}]{GHG}{GHG}{greenhouse gases}
\newabbreviation[group={Acronyms}]{GSA}{GSA}{global sensitivity analysis}
\newabbreviation[group={Acronyms}]{GWP}{GWP}{global warming potential}

@@

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{non-energy demand}
\newabbreviation[group={Acronyms}]{NG}{NG}{natural gas}
\newabbreviation[group={Acronyms}]{NN}{NN}{neural network}
\newabbreviation[group={Acronyms}]{NRE}{NRE}{non-renewable energy}
\newabbreviation[group={Acronyms}]{NSC}{NSC}{naphtha steam cracker}

@@

%% R
\newabbreviation[group={Acronyms}]{RE}{RE}{renewable energy}
\newabbreviation[group={Acronyms}]{RL}{RL}{reinforcement learning}

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor Critic}
\newabbreviation[group={Acronyms}]{SDGs}{SDGs}{Sustainable Development Goals}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{small modular reactor}
